---
title: "R Notebook"
output: html_notebook
---
Unfortunately, I did not complete the task for the script. I was not able to convert latitude and longitude to numeric and eliminate the parenthesis, there were a few NA I was able to eliminate. 

1. Read the cleaned data into R.

```{r}
clean_janitor_meteorite_data_separate_filter
```

2. Find the names and years found for the 10 largest meteorites in the data.

```{r}
clean_janitor_meteorite_data_separate_filter %>% 
  select(name,mass_g,year) %>%
   slice_max(mass_g, n = 10)


```

3.Find the average mass of meteorites that were recorded falling, vs. those which were just found.
```{r}

average_fall <-clean_janitor_meteorite_data_separate_filter %>%                #Felll,Found 2 average + comparacion
  group_by(fall) %>% 
  summarise(fall, mean_mass = mean(mass_g)) %>%  
  arrange(mean_mass) 
  
average_fall

```
4.Find the number of meteorites in each year, for every year since 2000.
```{r}
meteorites_by_year <- clean_janitor_meteorite_data_separate_filter %>% 
  select(name,year) %>% 
  filter(year >= 2000) %>% 
   arrange(desc(year)) 

meteorites_by_year

#summarise(meteorites_by_year,year = n())
```
5.Write a function called get_meteorite_count() that takes in two arguments: a dataframe and a year, and returns the phrase “In (input_year), there were (number of meteorites that year) meteorites.” IF there are 1 or more meteorites that year. If there are no meteorites in the year, return the phrase “As far as we know, there were no meteorites that year”.

```{r}

fire_ball <- c("313", "4", "2")
names_day <- c("john","Johanes","johana")
 fire_stones <- data.frame(fire_ball, names_day)

year <- c("1000", "1492", "1629")

x>=1000




get_meteorite_count()<- function(x,y){
  if(x >= 1000){
    return (paste("In  ,there were  meteorites"))}
    else "As far as we know, there were no meteorites that year"
}
get_meteorite_count(900)


```

6.Write down ideas for how the function you’ve written could be improved and how you could test that the function works as it should. Please keep these ‘test plans’ in the final .Rmd, especially if you are completing the PDA.






7.Write a unit test for your function to check whether non-numeric inputs (character and logical) for the year argument return an error.







8.Improve your function based on the result of your test. Instead of going back and changing the function, please create a new function that is the improved version called refactor_get_meteorite_count(). Test your function to make sure it now gives an error when you input a logical or character value as the year. Hint: You can use the stop function to create your own error message.