---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
library(modelr)
library(broom)
library(infer)

```

1 MVP

Load the housing_prices.csv data set and undertake an initial exploration of the data. You will find details on the data set on the relevant Kaggle page

```{r}
hp <- read_csv('data/housing_prices.csv')
hp
```

```{r}
summary(hp)
```

We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use ggpairs() to investigate correlations between these two variables.

```{r ,message = FALSE, warning = FALSE}
corrplothp<- ggpairs(hp)+ theme_grey()


# save for better look
png('hp.png', height=1000, width=1000)
print(corrplothp)
dev.off()

corrplothp
```
total_rooms (y) correlated with total_bedrooms(x) but no make sense no all bedrooms are rooms, so the independent should be total_rooms

```{r}
hp %>% 
  ggplot(aes(total_rooms, y = total_bedrooms))+
  geom_point()+
   geom_smooth(method = "lm", se = FALSE)
  

```
```{r}
hp %>% 
  ggplot(aes(total_bedrooms, y = total_rooms))+
  geom_point()+
   geom_smooth(method = "lm", se = FALSE)
```


So, we do find significant correlations. Let’s drop total_bedrooms from the dataset, and use only total_rooms going forward.
```{r}
hp_nobedroom <- hp %>% 
  select(-total_bedrooms)

hp_nobedroom
```

We are interested in developing a regression model for the median_house_value of a house in terms of the possible predictor variables in the dataset.
Use ggpairs() to investigate correlations between median_house_value and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r, message = FALSE, warning = FALSE}
corrplothouse_val<- ggpairs(hp_nobedroom)+ theme_grey()

png('corrplothouse_val.png', height=1000, width=1000)
print(corrplothp)
dev.off()



corrplothouse_val
```

_median_houses as predictor = x, doesn't work is the dependent variable (y)

_The variable 'ocean_proximity' makes unnecessary the variables longitude, latitude




Perform further ggplot visualisations of any significant correlations you find.

```{r}
hp_nobedroom %>%
  ggplot(aes(x = ocean_proximity, y = median_house_value)) +
  geom_boxplot()
  
#The location is a independent variable that makes that median_house_value increase
```

```{r}
hp_nobedroom %>%
  ggplot(aes(x = total_rooms, y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# The total_rooms is not a strong correlation
```


```{r}
hp_nobedroom %>%
  ggplot(aes(x = median_income , y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# median_income is not a predictor variable when median_house_value is a dependent variable
```





Shortly we may try a regression model to fit the categorical predictor ocean_proximity. Investigate the level of ocean_proximity predictors. How many dummy variables do you expect to get from it?










Start with simple linear regression. Regress median_house_value on median_income and check the regression diagnostics.
y ~x

```{r}
hp_nobedroom %>%
  ggplot(aes(x = median_house_value, y = median_income)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

#As the median_house_value increase, the median_income increase
```
```{r}

house_income <- lm(median_house_value ~ median_income, data = hp_nobedroom)

autoplot(house_income)
```

```{r}
summary(house_income)
```

  _ The coefficients shows that each time the median_income increase in 39987 currency units the intercept/ median_house_value increase in 45457 currency units.




Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.




```{r}
house_income2 <- lm(median_house_value ~ median_income + ocean_proximity, data = hp_nobedroom)

autoplot(house_income2)
```



```{r}
summary(house_income2)
```

_ The regression shows that the location is important in how the intercept is increasing, except when is inland.



























