---
title: "R Notebook"
output: html_notebook
---
Homework

```{r}
library(tidyverse)
library(janitor)




```



```{r}
marketing <-  read_csv('data/mall_customers.csv') %>% clean_names()
marketing
```

Marketing  : spending_score and annual_income


```{r}
marketing_subset <- marketing %>% 
  select(c(spending_score_1_100,annual_income_k))
```
# Starting Point

```{r}
ggplot(marketing_subset, aes(x = annual_income_k , y = spending_score_1_100))+
  geom_point()
```
From the graph the first impression is that there are 5 groups.
There is a small group of customers with low income but high spending_score;there is another with low -medium income and low-medium spending_score.
The third group and, perhaps the most interesting,there is a group of customers with medium income  ( around 50 k per year) and medium spending_score and very concentrate from the others 4 groups.
The last two groups are these customers with high income, one with also a high spending_score and another low spending income.
These last three groups could be the targeting. 
 
 
Scale the data

```{r}
marketing_scaled <- marketing_subset %>% 
  mutate(across(everything(), scale))
```

Making a cluster
```{r}
# we run 5 cluster for 5 groups
marketing_cluster5 <- kmeans(marketing_scaled,
                             center = 5,
                             nstart = 25)
```



```{r}
library(broom)
```

```{r}
tidy(marketing_cluster5)
```
```{r}
augment(marketing_cluster5, marketing_scaled)
```
```{r}
 glance(marketing_cluster5)
```





k value
marketing5


```{r}
k_clusters5 <-  tibble(k =1:40) %>% 
  mutate(
    kclust = map(k, ~ kmeans(x = marketing_scaled, centers = .x, nstart = 25)),
    tidied = map (kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, ~augment(.x, marketing_scaled))
  )

```

```{r}
library(factoextra)
```

Personally, I feel the silhouette coefficient method  is the most visible, I run two methods : Silhouette and Elbow

```{r}
fviz_nbclust(marketing_scaled,
             kmeans,
             method = 'silhouette',
             nstart = 25)
```

```{r}
fviz_nbclust(marketing_scaled,
             kmeans,
             method = 'wss',
             nstart = 25)
```
As I said above, from the plot I thought there were 5 groups, the silhouette method marks  that there are 5 clusters, so I believe that the clustering fit for the data. Personally, I feel that the second plot with the Elbow method is unclear to do a confirmation because the cluster looks is marked k = 3/4. I will run a third plot/method to be more sure.

```{r}
fviz_nbclust(marketing_scaled,
             kmeans,
             method = 'gap',
             nstart = 25)

```
According with the GAP Statistic method, the optimal cluster is 1!.

#Run few plots with different k values 5,3.


```{r}
k_clusters5 %>% unnest(augmented) %>% # explore column
  filter(k == 5) %>%   # filter for optimal k
ggplot()+
  aes(x = annual_income_k, y = spending_score_1_100,
      colour = .cluster)+
  geom_point()
```
This plot is like a repetition of the first plot with colours

```{r}
k_clusters5 %>% 
  unnest(augmented) %>% 
  filter(k ==5) %>% 
  group_by(.cluster) %>% 
  summarise(
    mean(annual_income_k),
    mean(spending_score_1_100),
    #sd(annual_income_k),
   # sd(spending_score_1_100)
  )
```
The visualization and the average score marks that there is a group with positive annual income but negative spending_score, that could be the targeting group. There is another group with positive annual income but its spending_score is , also, positive . In my opinion that means that they can no expend more moneyin our products.


```{r}
k_clusters5 %>% unnest(augmented) %>% # explore column
  filter(k == 3) %>%   # filter for optimal k
ggplot()+
  aes(x = annual_income_k, y = spending_score_1_100,
      colour = .cluster)+
  geom_point()
```
This second plot is interesting because adds three 'points' of the medium to the high annual income and lower spending_score.Also, the medium group of medium income and spending is add to the group of lower income  and low or high spending_score. Leaving the 'green' cluster : high annual income and low spending_score  like the targeting group.


```{r}
k_clusters5 %>% 
  unnest(augmented) %>% 
  filter(k ==3) %>% 
  group_by(.cluster) %>% 
  summarise(
    mean(annual_income_k),
    mean(spending_score_1_100),
    #sd(annual_income_k),
    #sd(spending_score_1_100)
  )
```







