---
title: "R Notebook"
output: html_notebook
---
# First step

```{r}
library(tidyverse)
read_csv("data/books.csv")
books <- read_csv("data/books.csv")
```


```{r}
books
```
# Dimensions

```{r}
dim(books)
```
```{r}
length(books)
```
# Colums
```{r}
ncol(books)
```
# Rows
```{r}
nrow(books)
```
# Names
```{r}
names(books)
```
# improve columns'names
```{r}
rename_books <-books %>% 
 rename("Row_id" = "rowid", "Book_id" = "bookID", "Title" = "title", "Authors"= "authors", "Average_rating" = "average_rating", "Isbn" = "isbn", "Isbn_13" = "isbn13", "Language_code" = "language_code", "Num_pages" = "num_pages", "Ratings_count" = "ratings_count", "Text_reviews_count" = "text_reviews_count","Publication_date" = "publication_date", "Publisher" = "publisher")
 names(rename_books)
```
# After check the columns, I think  there should be another variables like Age,Category and Synopsis. In order to improve collection. 

```{r}
rename_books
```
# Personally, I feel more confortable to have the first letter of the variable in Capital or using PascalCase.However, in order to use the best coding practice I will use snake_case and change again the variables names.
```{r}
rename_books2 <- rename_books %>% 
 rename("row_id" = "Row_id", "book_id" = "Book_id", "title" = "Title", "authors"= "Authors", "average_rating" = "Average_rating", "isbn" = "Isbn", "isbn_13" = "Isbn_13", "language_code" = "Language_code", "num_pages" = "Num_pages", "ratings_count" = "Ratings_count", "text_reviews_count" = "Text_reviews_count","publication_date" = "Publication_date", "publisher" = "Publisher")
```

```{r}
rename_books2
```

Authors by language
```{r}
language_data <- select(rename_books2, language_code, authors, title)
language_data
```
# Try filter the books with a different Language_code to "eng","en-US".
```{r}
filter(rename_books2, language_code != c("eng", "en-US"))
```

```{r}
filter(rename_books2,language_code == c("spa", "fre"))
```

```{r}
select(rename_books2,title,authors,language_code)
```

```{r}
select(rename_books2,authors,title,average_rating)
```

```{r}
select(rename_books2,authors,title,average_rating) %>% 
  arrange(desc
          (average_rating))
```

```{r}
select(rename_books2, authors, title, average_rating)%>% 
  filter(average_rating <= 4.30)
```
#ISBN,ISBN13. they marks country publishing, publisher, year..... If start by 0,1 publish in English but 84 means Spain


```{r}
select(rename_books2,authors,title,isbn,isbn_13)
```
# How to know all the books publish in Spain/Spanish
```{r}
spanish_book <- select(rename_books2,authors,title,isbn,isbn_13)%>% 
  filter(isbn >= 8400000000 & isbn <= 8499999999)


```


# The idea of this tibble was to obtain the publishers which language_code were Spanish ("spa") or French ("fre")
```{r}
select(rename_books2,authors,title,language_code,isbn) %>% 
  filter(language_code %in% c("spa","fre"))
```
# The idea of this tibble was to obtain the publishers which language_code were anyone except English, I satarted wiht these two "eng" and ""en-US", because I saw there was a issue and I was not able to fix it, I stoped here.
```{r}
#Did not work
# select(rename_books2,publisher,language_code) %>% 
#   filter(language_code != c("eng","en-US"))
#Did not work
 # select(rename_books2,publisher,language_code) %>% 
 #  filter(language_code != %in% c("eng","en-US"))


#Correct answer
select(rename_books2,publisher,language_code) %>% 
  filter(!language_code %in% c("eng","en-US"))

```

# Best average by author. It should be the best but I dont know why I get the worst
```{r}

best_rating <- rename_books2 %>% 
  group_by(authors) %>% 
  summarise(mean_average = mean(average_rating)) %>% 
  arrange(mean_average)

best_rating

```
Again, I get the worst even if I change few parameters. Anyway do not publish Andrew Hunt

```{r}

best_rating <- rename_books2 %>% 
  group_by(authors) %>% 
   summarise(mean_average = mean(average_rating)) %>% 
    arrange(desc(mean_average)) %>% 
    tail(5)

best_rating

```

#Text review by Author  

```{r}
select(rename_books2,authors,title,text_reviews_count,publication_date)
```

```{r}

best_review <- rename_books2 %>%
  group_by(authors)%>%
  summarise(mean_review = mean(text_reviews_count)) %>% 
  arrange(desc(mean_review))
  head(5)
 
best_review
  
```
#How joint each author with the means of his/her rating and review

```{r}
#select(rename_books2,authors,best_review,best_rating)

 perhaps_better_author <- rename_books2 %>% 
   group_by(desc(authors))%>%
   summarise(best_rating,best_review) 


perhaps_better_author

# Doesnt look like the better author

```

#Create a new table for century. If the books were published in the XX century

```{r}
last_century_publication <-select(rename_books2, authors, title, publication_date) %>% 
  mutate(last_century_publication = publication_date <= 12/12/1999)
#It did not work
```

```{r}
select(rename_books2, authors, title, last_century_publication)%>%
  filter(last_century_publication = TRUE)
```

EXPLICACIONES/ RESOLUCION DUDAS  SIGUIENTE LUNES
```{r}
books( %>% )
summary() # da bastante informacion sobre los datos
```
```{r}
books %>% 
    glimpse() # Generic view data
```

```{r}
books %>% 
  select(authors)

books %>% 
  distinct()#colapse when authors is repeated

books %>% 
  count(authors) %>% 
  #little check
  summarise(n_original_rows = sum(n))

#Gareth Which author wrote the more pages
book_data_sm %>% # Books %>% 
  select(authors, num_pages) %>%
  # After running once, Anonymous is included, should be removed
  filter(authors != "Anonymous") %>%
  group_by(authors) %>%
  # Taken from stack overflow, couldn't get it working
  summarise_each(funs(first(na.omit(.)))) %>%
  arrange(desc(num_pages)) %>%
  slice_head(n = 10)
  # summarise_each(funs(first(na.omit()))) %>% 



book_data_sm %>% # Books %>% 
  select(authors, num_pages) %>%
  # After running once, Anonymous is included, should be removed
  filter(authors != "Anonymous") %>%
  group_by(authors) %>%
  slice_max(num_pages, n = 1)

#SEPARAR SI HAY MAS DE UN AUTOR
book_data_sm %>% # Books %>% 
  select(authors, num_pages) %>%
separate(col = authors, into = c("primary_author", "supporting_authors_illustrations"), sep ="/")



books %>%
  select(authors, num_pages) %>%
  # will cover separate this afternoon :) 
  separate(col = authors, into = c("primary_author", "supporting_authors_illustrators"), sep = "/",extra = "merge") %>% 
  # After running once, Anonymous is included, should be removed
  filter(primary_author != "Anonymous") %>%
  group_by(primary_author) %>%
  summarise(total_pages = sum(num_pages)) %>% 
  arrange(desc(total_pages)) %>%
  slice_head(n = 10)











```











