---
title: "R Notebook"
output: html_notebook
---

Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
library(tidyverse)
library(janitor)
library(infer)



ames<-read_csv("data/ames.csv") %>% clean_names()

names(ames)
view(ames)
```


Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
lot_area_dis <- ames %>% 
  ggplot(aes(x=lot_area))+
  geom_histogram()
  
lot_area_dis
#Answer. for me , it looks like that it is, with an area very demanding maybe for the commodities and the housing price.  And low demand in areas were the price is around 170000 ??
```





Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
# I understood that all the houses are sold, so the size should 2930 but is not, there is something wrong and the whole HW is wrong when I leave the size as 2930 without any reps, so I changed


bootstrap_sampling_ames <- ames %>% 
  rep_sample_n(size = 500,replace = TRUE, reps = 1000) %>% 
  summarise(mean_lot_area = mean(lot_area))


bootstrap_sampling_ames
```
```{r}
bootstrap_sampling_ames %>% 
  ggplot(aes(x = mean_lot_area))+
  geom_histogram(col = 'white', fill = 'steel blue', alpha = 1)
```
Answer
```{r}
bootstrap_distn <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn %>%
  visualise(bins = 30)
```

Task 4.
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
ci_95 <-bootstrap_sampling_ames %>% 
  summarise(mean = mean(mean_lot_area),
            lower_bound = quantile(mean_lot_area, probs = 0.025),
            upper_bound = quantile(mean_lot_area, probs = 0.975))
  
  
   ci_95      #mean   lower_bound upper_bound
             #10149.56	9567.744	10955.98	
```
```{r}


infer_sampling_ames <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 1000, type = 'bootstrap') %>% 
  calculate(stat = 'mean')

infer_sampling_ames
```
```{r}


infer_ci_95 <- infer_sampling_ames %>% 
  get_confidence_interval(level = 0.95, type ='percentile')


infer_ci_9  #lower_ci  upper_ci
             #9879.15	10433.61
```

```{r}
# visualise

infer_sampling_ames %>% 
  visualise(bins = 30)+
  shade_ci(endpoints = infer_ci_95)

```
Answer
```{r}
lot_area_ci95 <- bootstrap_distn %>%
  get_ci(level = 0.95, type = "percentile")
lot_area_ci95
```

```{r}
bootstrap_distn %>%
  visualise(bins = 30) +
  shade_ci(endpoints = lot_area_ci95)
```

Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
ci_99 <-bootstrap_sampling_ames %>% 
  summarise(mean = mean(mean_lot_area),
            lower_bound = quantile(mean_lot_area, probs = 0.005),
            upper_bound = quantile(mean_lot_area, probs = 0.995))
  
  
   ci_99 
```
Anwer

```{r}
lot_area_ci99 <- bootstrap_distn %>%
  get_ci(level = 0.99, type = "percentile")
lot_area_ci99
```

```{r}
bootstrap_distn %>%
  visualise(bins = 30) +
  shade_ci(endpoints = lot_area_ci99)
```


Task 6.
Calculate the point estimate of the mean(lot_area)
```{r}
point_est <-  infer_sampling_ames %>% 
  summarise(mean = mean(stat))


point_est
```
```{r}

ames %>% 
  summarise(mean(lot_area))
```
```{r}
mes %>%
  summarise(point_est = mean(lot_area))
```
```{r}
bootstrap_distn %>%
  summarise(point_est = mean(stat))
```

2 Extension


Task 1.
Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].

```{r}

h_before_1920 <- ames %>% 
  filter(year_built <= 1920)



h_before_1920
```
```{r}
# first Bootstrapping

bootstrap_s_h_before_1920 <- h_before_1920 %>% 
  rep_sample_n(size = 100, replace = TRUE, reps = 50) %>% 
  summarise(mean_lot_area = mean(lot_area))


bootstrap_s_h_before_1920
```

```{r}
ci_95 <- bootstrap_s_h_before_1920 %>% 
  summarise(mean = mean(mean_lot_area),
            lower_bound = quantile(mean_lot_area, probs = 0.025),
            upper_bound = quantile(mean_lot_area, probs = 0.975))
  

ci_95   


#             mean  lower_bound   upper_bound
#100,  50 : 9452.524	8598.653	10237.03	
#100, 500 : 9453.733	8562.634	10640.83
#100,5000 : 9465.193	8508.489	10625.52	
```
```{r}
ames_before_1920 <- ames %>%
  mutate(before_1920 = as.numeric(year_built < 1920))
```
To investigate the effect of number of reps, let’s generate five different bootstrap sampling distributions

```{r}
bootstrap_distn_200 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 200, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_1000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_10000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_30000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 30000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn_50000 <- ames_before_1920 %>%
  specify(response = before_1920) %>%
  generate(reps = 50000, type = "bootstrap") %>%
  calculate(stat = "mean")
```
Calculate point estimates:
```{r}
point_est <- ames_before_1920 %>%
  summarise(point_est = mean(before_1920))
point_est
```

```{r}
point_est <- bootstrap_distn_50000 %>%
  summarise(point_est = mean(stat))
point_est
```
```{r}
before_1920_ci95_200 <- bootstrap_distn_200 %>%
  get_ci(level = 0.95, type = "percentile")
before_1920_ci95_200
```
```{r}
bootstrap_distn_200 %>%
  visualise(bins = 30) +
  shade_ci(endpoints = before_1920_ci95_200)

```











