---
title: "R Notebook"
output: html_notebook
---
```{r}
library(GGally)
library(ggfortify)
library(modelr)
library(tidyverse)

house_prices <- read_csv('data/kc_house_data.csv')

glimpse(house_prices)
```

```{r}
head(house_prices)
```

```{r}
summary(house_prices) # just in case there is NA
```
I have diced not remove or split the variables.

Question3.
 # First , check possible predictors
```{r}
skimr::skim(house_prices) %>% 
  view()
```
 
 #problems with id, removed it
 
```{r}
house_prices_trim <-  house_prices %>% 
  select(-c(id,sqft_living15,sqft_lot15,zipcode))

house_prices_trim
```
  _ggpairs in white and blank didn't work so I changed condition as.character to try to make a plot in colour
```{r}
house_prices_trim <- house_prices_trim %>% 
  mutate(condition = as.character(condition))

```
 
```{r message=FALSE}
house_prices_trim %>% 
  dplyr::select(price, everything()) %>% 
  ggpairs(aes(colour = condition))
```

Note> Problems with visualization plot , try to save as image , in case I can see better.
```{r}

image <- house_prices_trim %>% 
  dplyr::select(price, everything()) %>% 
  ggpairs(aes(colour = condition))

png('image.png', height=1000, width=1000)
print(image)
dev.off()
```
Regression model_4 predictors
price(y)- dependent variable

```{r}
mod1 <- lm(price ~ view, dat = house_prices_trim)
summary(mod1)
```
The R2 is 0.15 ( a bit low), so only 15 %  the variance in price of a house is based on view. However, the predictor is highly significant, so we can think in a good model ( strange).
The residual standard error is 336900, in terms of average error in house price I would say that is not very good.

```{r}
mod2 <- lm(price ~ floors, dat = house_prices_trim)
summary(mod2)
```
The R2 is 0.06 ( very low), so only 6 %  the variance in price of a house is based on number of floors. However, the predictor is highly significant, so we can think in a good model ( strange).
The residual standard error is 354800, in terms of average error in house price I would say that is not very good.

```{r}
mod3 <- lm(price ~ condition, dat = house_prices_trim)
summary(mod3)
```
The R2 is 0.0013 ( very low),condition of the house almost no affect the variance in price of a house . However, the predictor is highly significant, so we can think in a good model ( strange).
The residual standard error is 366900, in terms of average error in house price I would say that is bad.



```{r}
mod4 <- lm(price ~ floors, dat = house_prices_trim)
summary(mod4)
```




















































