---
title: "R Notebook"
output: html_notebook
---
```{r}
 library(tidyverse)
```
```{r}
library(CodeClanData)
library(ggplot2)
```




2 MVP
2.1 Part 1
Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.


```{r}
qb_revenue_breakdown
```
```{r}

qb_revenue_breakdown %>% 
  ggplot(aes(x = Product, y = Revenue, fill = Year)) +
              geom_col()

```
Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).


```{r}
qb_monthly_sales
```

```{r}
qb_monthly_sales %>% 
  filter(Cashflow == 'Kwikbit Unit 1 Sales') %>% 
  ggplot(aes(x = Date, y = Amount))+
  geom_line()

```
Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>% 
  filter(Cashflow == 'Total Revenue'| Cashflow == 'Cost') %>% 
  ggplot(aes(x = Date, y = Amount, group = Cashflow))+
  geom_line(aes(colour = Cashflow))
  

```
Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}

qb_competitors %>% 
   ggplot(aes(x = Year, y = Revenue, group = Company))+
     geom_area(aes(fill = Company))
```
Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
qb_competitors
```

```{r}
qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company)) +
  geom_line(aes(colour = Company))
```
Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
device <- qb_device_data
```
```{r}
device %>% 
  mutate(time = hours + mins/60) %>% 
  ggplot(aes(x = time , y = counts, colour = device ))+
  geom_line()+
  facet_wrap(id~device)

```
2.2 Part 2
Question 1.
Take the plots that you produced in part one and now polish them by:
Adding appropriate labels
Changing the scales and coordinates when appropriate.
Applying a unified theme, which is described below:
Graphs should have white backgrounds, and use colour sparingly.
There should be faint grid lines.
Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
All plots should use colours from the following company colour scheme.

```{r}
# company_theme <- theme %>% 
# (plot.title = element_text(size = 12,face = "bold"),panel.background = element_rect(fill = "white"),axis.text.x = element_text(angle = 45, hjust = 1))
```


q1
```{r}
# I did not use the company colours because it does not look good 

qb_revenue_breakdown %>% 
  ggplot(aes(x = Product, y = Revenue, fill = Year)) +
  labs(title= 'Annually Revenue by device')+
  geom_col(position = 'dodge')+
  scale_y_continuous(labels = scales::comma) +
  theme(plot.title = element_text(size = 12,face = "bold"),panel.background = element_rect(fill = "white"),axis.text.x = element_text(angle = 45, hjust = 1))+
  coord_flip()

  
```
Q2
```{r}

qb_monthly_sales %>% 
  filter(Cashflow == 'Kwikbit Unit 1 Sales') %>% 
  ggplot(aes(x = Date, y = Amount))+
  labs(y = 'Sales', title = ' Yearly Sales' )+
  geom_line()
```
q3
```{r}
#  

qb_monthly_sales %>% 
  filter(Cashflow == 'Total Revenue'| Cashflow == 'Cost') %>% 
  ggplot(aes(x = Date, y = Amount, group = Cashflow))+
  labs(title = ' Revenue - Cost')+
  scale_y_continuous(labels = scales::comma) +
  scale_colour_manual(
    values = c(
      "TotalRevenue" = "#F9A472",
      "Cost" = "#50434F"))+
  theme(plot.title = element_text(size = 12,face = "bold"),
        panel.background =  element_rect(fill = "white"))+
  geom_line(aes(colour = Cashflow))


```




```{r}
qb_monthly_sales %>% 
  filter(Cashflow == 'Total Revenue'| Cashflow == 'Cost') %>% 
  ggplot(aes(x = Date, y = Amount, group = Cashflow))+
  labs(title = ' Revenue - Cost')+
  scale_y_continuous(labels = scales::comma) +
  scale_colour_manual(
    values = c(
      "TotalRevenue" = "#F9A472",
      "Cost" = "#50434F"))+
  theme(plot.title = element_text(size = 12,face = "bold"))+
        #panel.background =  element_rect(fill = "white"))+
  geom_line(aes(colour = Cashflow))
```
Q4
```{r}
# I did not use the company colours because it does not look good 


qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company))+
  labs(title ='Market Evolution')+
  scale_y_continuous(labels = scales::comma) +
  # scale_fill_manual(
  #   values = c(
  #     "qikbit1" = "#50434F",
  #     "competitor1" = "#E89FE9",
  #     "competitor2" = "#B6A7B5",
  #     "competitor3" = "#F9A472",
  #     "competitor4" = "#BD7040"))+
  theme(plot.title = element_text(size = 12,face = "bold"),
        panel.background =  element_rect(fill = "white"))+
   geom_area(aes(fill = Company))

```
Q5
```{r}
# I did not use the company colours because it does not look good 

qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company)) +
  labs(x = 'Sales', title = 'Sales by companies')+
   scale_y_continuous(labels = scales::comma) +
  # scale_colour_manual(
  #   values = c(
  #     "qikbit1" = "#50434F",
  #     "competitor1" = "#E89FE9",
  #     "competitor2" = "#B6A7B5",
  #     "competitor3" = "#F9A472",
  #     "competitor4" = "#BD7040"))+ with Company's colours  is no clear
  theme(plot.title = element_text(size = 12,face = "bold"),
        panel.background = element_rect(fill = "white"))+
  geom_line(aes(colour = Company))
  

```

Q6
```{r}
device %>% 
  mutate(time = hours + mins/60) %>% 
  ggplot(aes(x = time , y = counts, colour = device ))+
  labs(x = 'Hours Used', y = 'Steps', title = 'Efficiency')+
   scale_y_continuous(labels = scales::comma) +
  geom_line()+
  scale_colour_manual(
    values = c(
      "qikbit1" = "#50434F",
      "competitor1" = "#E89FE9",
      "competitor2" = "#B6A7B5",
      "competitor3" = "#F9A472"))+
  theme(plot.title = element_text(size = 12,face = "bold"),
        panel.background = element_rect(fill = "white"))+
  facet_grid(id~device) 
  
  
  
  

```


















