---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)

data("msleep")

view(msleep)
```

Question 2.
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

alpha level :0.05
H0 :  mean_sleep_total = mean_sleep_jabberwockies
HA :  mean_sleep_total != mean_sleep_jabberwockies

```{r}
#visualize the sleep_total - average is close to 10h
msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_boxplot(col = "red", fill = 'steel blue')
```

```{r}
#calculate average sleep.

observed_stat_total <-  msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat_total #10.43373
```


```{r}
#null distribution

null_distribution_total_sleep <-  msleep %>%
  specify(response = sleep_total) %>% 
  hypothesise(null= 'point', mu = 7) %>% 
  generate(resps= 1000, type = 'bootstrap') %>% 
  calculate(stat = 'mean')

null_distribution_total_sleep   # stat 6.953012
```
```{r}
# overlay visual  and direction. From my previous visualization -on top-I concluded that the direction have to be 'greater/rigth'

null_distribution_total_sleep %>% 
  visualise(bins = 30)+
  shade_p_value(obs_stat =observed_stat_total$mean_sleep_total,
                direction = 'right')

```
```{r}
#p_value
null_distribution_total_sleep %>% 
get_p_value(obs_stat = observed_stat_total$mean_sleep_total,
                direction = 'right')  

# p_value is 0, I did wrong is 1 if I changed to less but I think I did correctly 
```
Answer.
With a p-value (0) less than our significance level (0.05) we may reject the null hypothesis in favour of the alternative hypothesis: the average total sleep for all the animal is different from the average sleep forJabberwockies

    Question 3.
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

# two independent samples, average = mean will be compare

alpha : 0.05
HO :avg_sleep_omnivores - avg_sleep_herbivores > 0
HA :avg_sleep_omnivores - avg_sleep_herbivores = 0

```{r}
herbi_omni <- msleep %>% 
  select(name,vore,sleep_total) %>% 
  filter(vore == c ('herbi','omni'))

herbi_omni
```

```{r}
#Visual , looks like that in avg omni sleep more than herbi
herbi_omni %>% 
  ggplot(aes(x = vore, y = sleep_total))+
  geom_boxplot()
```

```{r}
herbi_omni %>% 
  group_by(vore) %>% 
  summarise(mean_sleep = mean(sleep_total)) %>% 
  summarise("diff in means" = diff(range(mean_sleep)))

#diff_in_means 3.221538
```


```{r}
#observe_stat
observed_stat_compa <- herbi_omni %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = 'diff in means', order = c('herbi','omni'))




observed_stat_compa  #stat -3.221538
```

```{r}
null_distribution_compa <-  herbi_omni %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = 'independence') %>% 
  generate(reps = 1000, type = 'permute') %>% 
  calculate(stat = 'diff in means' , orde = c('herbi','omni'))

null_distribution_compa
```
```{r}
#visual

null_distribution_compa %>% 
  visualise(bins = 30)+
  shade_p_value(
    obs_stat = observed_stat_compa$stat,
    direction = 'right'
  )
```
```{r}
#get the p_value
null_distribution_compa %>% 
  get_p_value(
    observed_stat_compa$stat,
    direction = 'right'
  )

#p_value is 0.97
```

Answer.
With a p_values  close to 1, we do not have enough evidence to reject the null hypothesis; the average sleep for omnivores is higher than for herbivores



Question 4. Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.


alpaha ; 0.05
H0 :prop_domesticated -0.05 = 0
HA : prop_domesticated -0.05 !=0

```{r}
domesticated <- msleep %>% 
  filter(conservation = 'domesticated')

domesticated
```
```{r}
observed_stat_domesticated <- domesticated %>% 
  summarise(prop = n()/nrow(msleep))

observed_stat_domesticated  # prop 0.1204819
```
```{r}

```








1.2 Hypothesis testing - Defining the Hypothesis

Question 1.










Question 2.











Question 3.







1.3 Hypothesis Testing - Interpreting the results

    Question 1.
    Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07

With a p_value slightly superior to our significant level, we can not reject the null hypothesis about if the Coffee shop has problems  


    Question 2.
    Website company problem. Significance level: 0.01, p-value: 0.006

In this case, our p-value is less than our significant level, so we can reject the null hypothesis about the problems around the website company.


    Question 3.
    Manufacturing company problem. Significance level: 0.05, p-value: 0.55

With a P-value superior to to our significant level, we fail to reject the null hypothesis about the problems around the manufacturing company



