---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)

data("msleep")

view(msleep)
```

Question 2.
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

alpha level :0.05
H0 :  mean_sleep_total = mean_sleep_jabberwockies
HA :  mean_sleep_total != mean_sleep_jabberwockies

```{r}
#visualize the sleep_total - average is close to 10h
msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_boxplot(col = "red", fill = 'steel blue')
```

```{r}
#calculate average sleep.

observed_stat_total <-  msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat_total #10.43373
```


```{r}
#null distribution

null_distribution_total_sleep <-  msleep %>%
  specify(response = sleep_total) %>% 
  hypothesise(null= 'point', mu = 7) %>% 
  generate(resps= 1000, type = 'bootstrap') %>% 
  calculate(stat = 'mean')

null_distribution_total_sleep   # stat 6.953012
```
```{r}
# overlay visual  and direction. From my previous visualization -on top-I concluded that the direction have to be 'greater/rigth'

null_distribution_total_sleep %>% 
  visualise(bins = 30)+
  shade_p_value(obs_stat =observed_stat_total$mean_sleep_total,
                direction = 'right')

```
```{r}
#p_value
null_distribution_total_sleep %>% 
get_p_value(obs_stat = observed_stat_total$mean_sleep_total,
                direction = 'right')  

# p_value is 0, I did wrong is 1 if I changed to less but I think I did correctly 
```
Answer.
With a p-value (0) less than our significance level (0.05) we may reject the null hypothesis in favour of the alternative hypothesis: the average total sleep for all the animal is different from the average sleep forJabberwockies

    Question 3.
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

# two independent samples, average = mean will be compare

alpha : 0.05
HO :avg_sleep_omnivores - avg_sleep_herbivores > 0
HA :avg_sleep_omnivores - avg_sleep_herbivores = 0

```{r}
herbi_omni <- msleep %>% 
  select(name,vore,sleep_total) %>% 
  filter(vore == c ('herbi','omni'))

herbi_omni
```

```{r}
#Visual , looks like that in avg omni sleep more than herbi
herbi_omni %>% 
  ggplot(aes(x = vore, y = sleep_total))+
  geom_boxplot()
```

```{r}
herbi_omni %>% 
  group_by(vore) %>% 
  summarise(mean_sleep = mean(sleep_total)) %>% 
  summarise("diff in means" = diff(range(mean_sleep)))

#diff_in_means 3.221538
```


```{r}
#observe_stat
observed_stat_compa <- herbi_omni %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = 'diff in means', order = c('herbi','omni'))




observed_stat_compa  #stat -3.221538
```

```{r}
null_distribution_compa <-  herbi_omni %>% 
  specify(response = sleep_total, explanatory = vore) %>% 
  hypothesise(null = 'independence') %>% 
  generate(reps = 1000, type = 'permute') %>% 
  calculate(stat = 'diff in means' , orde = c('herbi','omni'))

null_distribution_compa
```
```{r}
#visual

null_distribution_compa %>% 
  visualise(bins = 30)+
  shade_p_value(
    obs_stat = observed_stat_compa$stat,
    direction = 'right'
  )
```
```{r}
#get the p_value
null_distribution_compa %>% 
  get_p_value(
    observed_stat_compa$stat,
    direction = 'right'
  )

#p_value is 0.97
```

Answer.
With a p_values  close to 1, we do not have enough evidence to reject the null hypothesis; the average sleep for omnivores is higher than for herbivores



    Question 4. Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.


alpaha ; 0.05
H0 :prop_domesticated -0.05 = 0
HA : prop_domesticated -0.05 !=0

```{r}
domesticated_prop <- msleep %>% 
  mutate(is_domesticated = if_else(conservation == 'domesticated',"domestic","no_domestic"))

domesticated_prop

```
```{r}
null_distribution_domes <- domesticated_prop %>% 
  specify(response = is_domesticated, success = 'domestic') %>% 
  hypothesise(null = 'point', p= 0.05) %>% 
  generate(reps = 1000, type = 'draw')
  #calculate(stat = 'prop')
null_distribution_domes
```

```{r}
observed_stat_domes <- domesticated_prop %>% 
  summarise(prop = n()/nrow(msleep))

observed_stat_domes
```
```{r}
null_distribution_domes %>% 
  visualise(bins = 30)+
  shade_p_value(obs_tat = observed_stat_domes, direction = 'both')
```








1.2 Hypothesis testing - Defining the Hypothesis

    Question 1.

 The test I would use is a 1 sample test proportion.Because there is only one sample (the coffee shop) and the question is a percentage.
 
H_0 : know the coffee shop  = 0.04 (40%). We can not reject the idea that the 40% of the city population knows about the coffee shop.

H_A : know the coffee shop != 0.04 (40%). It is unclear that the 40% of the city population  knows about the coffee shop.Could be more or less.

For this kind of test we will use for generate the null distribution a Draw method


    Question 2.

Although, the problem is about the location/position of a banner inside of the same website, so two versions of the same sample. I think I would use a 2 samples independent Hypothesis, because it is a comparison between two different groups and their proportion in use the banner.

H_0 : the better position for the banner is on top page. Group_B - Group_A = 0
     H_0 = 0
H_A : it is no clear that the better position for the banner is on top. Note, another question could be that it is not important the position for the banner. Group_B - Group_A != 0
     H_A != 0

I would use a hypothesis of independence and a null distribution  with a Permute method


    Question 3.

 The car manufacturer will investigate the drifted mean value of width of one specific car part. In this occasion, I would use a 1 sample test.
 I am using the word "drifted" for the 200 sample
 
 H_0 : average_width_drifted_car_parts - average_width_car_parts = 0
 
 H_A : average_width_drifted_car_parts - average_width_car_parts != 0
 
 
 As it was mentioned before, the parameter is the mean. So, for the null distribution I would use a bootstrap method  





1.3 Hypothesis Testing - Interpreting the results

    Question 1.
    Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07

  With a p_value slightly superior to our significant level, we can not reject , it is unclear, the null hypothesis about if the 40%  of the city population knows about the Coffee shop   


    Question 2.
    Website company problem. Significance level: 0.01, p-value: 0.006

  In this case, our p-value is less than our significant level, so we can reject the null hypothesis about the hypothesis where the right position for the banner is on top page.


    Question 3.
    Manufacturing company problem. Significance level: 0.05, p-value: 0.55

 With a P-value superior to to our significant level, we fail to reject (or we can not reject ) the null hypothesis about the drifted width in the car parts.



