---
title: "week05-day02HWNachoDeVicente"
output: html_notebook
---
```{r}
library(tidyverse)
library(CodeClanData)
backpack
```
Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.



Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


Backpacks weigth distribution by major

```{r}
backpack %>% 
  ggplot(aes(x = major , y = backpack_weight, fill = major), stat = 'identity')+
  geom_col(position = 'dodge')+
  coord_flip()
  
  
```


```{r}
backpack %>% 
  ggplot(aes(x = major, y = backpack_weight))+
  geom_point(aes(colour = major, shape = sex), size = 4)+
  coord_flip()
```
This dsitribution is by major and sex




Question 3.

Are there differences in backpack weight between sex?

Backpacks weigth distribution by sex
```{r}
backpack %>% 
  ggplot(aes(x = sex , y = backpack_weight), stat = 'identity')+
  geom_col(fill = 'light blue')
```
Women have more weight than men



Question 4.

What is the relationship between body weight and backpack weight?


```{r}
backpack %>% 
  ggplot(aes(x= body_weight , y = backpack_weight)) +
  labs(x = 'Body_weigth', y = 'backpack_weigth',title= 'Relations')+
  theme(plot.title = element_text(size = 16,face = "bold")) +
  geom_point(show.legend = FALSE)+
  geom_smooth(method = "lm", se = FALSE)

```

There is not a relation, as heavy is a person no necessary carry more backpack_weigth

Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.


```{r}
backpack %>% 
  ggplot(aes(x= body_weight , y = backpack_weight)) +
  labs(x = 'Body_weigth', y = 'backpack_weigth',title= 'Relations')+
  theme(plot.title = element_text(size = 16,face = "bold")) +
  geom_point(aes(shape = sex,show.legend = FALSE))+
  #geom_smooth(method = "lm", se = FALSE)+
  coord_flip()

```
The table shows that the data is concentrate and no a clear relation as heavy the person/ sex more weigth can carry






Question 6.
What proportion of students report back pain?

```{r}
group_by(Body)
count()
```








Question 7.

Is this proportion different between men and women?

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.






number of students
mutate(students =sum )
group_by()
count()




