---
title: "week05-day02HWNachoDeVicente"
output: html_notebook
---
```{r}
library(tidyverse)
library(CodeClanData)
backpack
```
Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.
```{r}
names(backpack)
```
```{r}
dim(backpack)
```



Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


Backpacks weight distribution by major

```{r}
backpack %>% 
  ggplot(aes(x = major , y = backpack_weight, fill = major), stat = 'identity')+
  labs(x= 'Backpack_weight',
       y = 'Major',
       title = 'Backpack_weigth by Major',
       subtitle = 'Daily University')+
  geom_col(position = 'dodge')+
  coord_flip()
  
  
```


```{r}
backpack %>% 
  ggplot(aes(x = major, y = backpack_weight))+
  geom_point(aes(colour = major, shape = sex), size = 4)+
  labs(x= 'Backpack_weight',
       y = 'Major',
       title = 'Backpack_weigth by sex',
       subtitle = 'Daily University')+
  coord_flip()
```
This distribution is by major and sex




Question 3.
Are there differences in backpack weight between sex?

```{r}
backpack %>% 
  ggplot(aes(x = sex , y = backpack_weight), stat = 'identity')+
  labs(x= 'sex',
       y = 'Backpack_weight',
       title = 'Backpack_weigth by sex',
       subtitle = 'Daily University')+
  geom_col(position = 'dodge',fill = 'light blue')
```

The data shows that male carry more backpack weight than female.
Note: However, if it is eliminated inside "geo_col" the 'position' the result is different.





Question 4.

What is the relationship between body weight and backpack weight?
```{r}
backpack %>% 
  ggplot(aes(x= body_weight , y = backpack_weight)) +
  labs(x = 'Body_weigth', y = 'backpack_weigth',title= 'Relations')+
  theme(plot.title = element_text(size = 16,face = "bold")) +
  labs(x= 'Body_weigth',
       y = 'Backpack_weight',
       title = 'Backpack_weigth by Body_weigth',
       subtitle = 'Daily University')+
  geom_point(colour = "Purple",show.legend = FALSE)+
  geom_smooth(method = "lm", se = FALSE)
```

There is not a relation, as heavy is a person no necessary carry more backpack_weigth

Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
backpack %>% 
  ggplot(aes(x= body_weight , y = backpack_weight)) +
  theme(plot.title = element_text(size = 16,face = "bold")) +
  labs(x= 'Body_weight',
       y = 'Backpack_weight',
       title = 'Relation Body/Backpack weight',
       subtitle = 'Daily University')+
  geom_point(aes(shape = sex,show.legend = FALSE), colour = "purple")+
  coord_flip()
```

The table shows that the body-weight is concentrate around 125lb and 175lb, and it is unclear a specific relation between the sex's weight and weight that this person can carry


Question 6.
What proportion of students report back pain?

```{r}
backpack %>% 
group_by(status) %>%
 summarise(counts = n()) %>%
  ggplot(aes(x = counts , y = 'back_problems' , fill = 'coral'), stat = 'identity') +
  geom_col(aes(show.legend = FALSE))
  
```



Question 7.

Is this proportion different between men and women?





Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.






