---
title: "R Notebook"
output: html_notebook
---
Question 1.
Find the weather forecast for the next three days online. Create a list of lists in which each inner list should be labelled with the name of the day of the week. Each inner list should contain named elements telling you the temperature, chance of rain and wind speed.



```{r}

total_weather <-list(
                "thursday" = list(temperature_max = 14, chance_of_rain_max = 0, wind_speed_max = 18) ,
                 "friday"  =list (temperature_max = 12, chance_of_rain = 60, wind_speed_max = 15) ,
                 "saturday" = list(temperature_max = 12, chance_of_rain = 60, wind_speed_max = 20)
)

total_weather


#
# thursday <-list(temperature_max = 14, chance_of_rain_max = 0, wind_speed_max = 18) ,
# friday  <-list (temperature_max = 12, chance_of_rain = 60, wind_speed_max = 15) ,
# saturday <- list(temperature_max = 12, chance_of_rain = 60, wind_speed_max = 20)
# 
# total_weather<- list(thursday,friday,saturday)
# 


```


Question 2.
Using the list you’ve just made find:

The chance of rain tomorrow
The wind speed on the day after tomorrow
The temperature tomorrow.

```{r}
#Chance of Rain
total_weather$thursday$chance_of_rain

#Wind Speed
total_weather[[2]][[3]]  #total_weather$friday$wind_speed

#Temperature
total_weather[[1]][[1]]

```
Question 3.
Find a 14 day forecast online and create a matrix of the forecasts for temperature, where each week is one row and columns correspond to days.

You will want to give a name to the matrix you create.

```{r}
#14 days = 2 weeks = 2 rows =7 column
#weather_m <- matrix(1:14, nrow = 2, ncol = 7)


weather_m <- matrix(c(14,12,12,13,13,10,6,8,9,10,12,14,7,5),nrow = 2, ncol = 7)


weather_m
```
Question 4.
From the matrix you just made select:

The third day of the second week
The whole second week
The first, third and fifth days in both weeks.

```{r}

#Third Day second week
weather_m [2,3]

#whole second week

weather_m [2,1:7]


#first,third,fifth days

weather_m[1:2,c(1,3,5)]

```
Question 5.
Write a function that pre-appends “The answer is:” to any character input, while for numeric input, it either just returns the number for numbers less than 10, or divides the number by 10 for numbers greater than 10. For anything else return “Invalid input”.
```{r}
#if else


answer <- function(x){
  if (x == chars){print("The answer is") }
   } else (x <= 10){print (x)
    }else (x>=10){print(x%%10)}
}

answer()

```


Question 6.
Write a function which checks if two vectors have the same elements.

If they have the same elements in the same order, return “Exactly the same”
If they have the same elements but in a different order, return “The same”
If they don’t have the same elements, return “Different”.
```{r}

cheker <- function (x,y){
  if ( x == y){print("Exactly the same")
   }else (x %in% y){print("The same")
      }else ( x != y){print("Different")}
}




```




