---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(tsibbledata)
library(lubridate)
library(ggplot2)
library(leaflet)
library(tsibble)

nyc_bikes_df <- nyc_bikes

nyc_bikes_df
```
```{r}
nyc_bikes_df <- nyc_bikes_df %>% 
  mutate(day = day(start_time),
         month = month(start_time),label = TRUE, abbr = FALSE,
          year = year(start_time))

nyc_bikes_df <- nyc_bikes_df %>% 
  mutate(age = (year - birth_year))


view(nyc_bikes_df)
```


```{r}
#durationtravel
nyc_bikes_df <- nyc_bikes_df %>% 
  mutate(duration_bike = as.duration(start_time - stop_time))

nyc_bikes_df 
  
```





        ### PATTERN BIKES HIRES

```{r}
nyc_bikes_df
```
HIRES BY DAY
```{r}
nyc_bikes_df %>% 
  group_by(day) %>% 
  count() %>% 
  summarise(n)
```

```{r}
nyc_bikes_df %>% 
  group_by(day) %>% 
  count() %>% 
  summarise(n) %>% 
  ggplot(aes(x= day, y = n))+
  geom_point()+
  scale_x_continuous(breaks = 1:31)+
  theme_bw()+
  labs(x = "Monthly days",
       y = "Number of users",
       title =" Our Clients")
  
```
```{r}

#No Work
nyc_bikes_df %>% 
  index(start_station) %>% 
  count() %>% 
  summarise(n) %>% 
  ggplot(aes(x= day, y = n))+
  geom_line()+
  scale_x_continuous(breaks = 1:31)+
  theme_bw()+
  labs(x = "Monthly days",
       y = "Number of users",
       title =" Our Clients")
```










HIRES BY MONTH

```{r}
nyc_bikes <- nyc_bikes_df %>% 
  mutate(month = month(start_time, label = TRUE, abbr = FALSE))
```

```{r}
nyc_bikes_df %>% 
  group_by(month) %>% 
  count() %>% 
  summarise(n) %>% 
  ggplot(aes(x= month, y = n))+
  geom_point()+
  theme_bw()+
  scale_x_continuous(breaks = 1:12)
```

### PATTERN RIDER

BY TYPE CLIENT

```{r}
nyc_bikes_df %>% 
  group_by(type) %>% 
  count()
```


```{r}
nyc_bikes_df %>% 
  group_by( type) %>% 
  ggplot(aes(x = type), stat = 'identity', colour = 'steelblue')+
  geom_bar()+
  labs(x = "type of contract",
       y = "Number of users",
       title =" Our Clients")+
  theme_bw()

```
We level of subscriber is higher than our casual customer
BY GENDER
```{r}
nyc_bikes_df %>% 
  count(gender)
```
```{r}

nyc_bikes_df %>% 
ggplot(aes(x = gender, fill = gender))+
  geom_bar()+
  labs(x = "Gender",
       y = "Number of users",
       title =" Our Clients")+
  theme_bw()
```
RIDER-TYPE

```{r}

nyc_bikes_df %>% 
  group_by(gender,type) %>% 
  count()

```

```{r}

nyc_bikes_df %>% 
  group_by(gender,type) %>% 
  ggplot(aes(x = type, fill = gender))+
  geom_bar()+
  coord_flip()+
labs(x = "Number of users",
       y = "type of Contract",
       title =" Our Clients")+
  theme_bw()

```
AGE

```{r}
nyc_bikes_df %>% 
  count(age <= 90)
```


```{r}
nyc_bikes_df %>%
  ggplot(aes( x= age, fill = gender))+
  geom_histogram(position = 'dodge', bins = 30)+
  labs(x = "Users by age",
       y = "type of Contract",
       title =" Our Clients")+
  theme_bw()
```


```{r}
nyc_bikes_df %>%
ggplot(aes(x = gender, y = age, color = gender)) + 
  geom_point() + 
  facet_wrap(~type) + 
  scale_y_continuous(breaks = c(15,20,30,40,50,60,70,80,90,100,110,120,130,140))+
    scale_color_manual(values=c('#E69F00', '#56B4E9', 'steelblue'))+
    labs(x = "Users by gender",
       y = "Age",
       title =" Our Clients")+
  theme_bw()
```
Why We have no real data from two subscribers?they said they have more than 130 years-old(we should improve our register system) it is interesting that we have subscribers  dont share gender, feel confortable?, it is a problem during register?


###Busiest months


```{r}
nyc_bikes_df %>% 
  count(month)

#geom_line to show the evolution using the service
#august is more used
```

```{r}
nyc_bikes_df %>% 
  ggplot(aes(x = month))+
  geom_bar()+
  scale_x_continuous(breaks = 1:12)+
 labs(x = "Users by month",
       title =" Our Clients")+
  theme_bw()
```
Good weather, tourist visit?


```{r}
nyc_bikes_df %>% 
  ggplot(aes(x = month,y = type, colour = gender)) +
  geom_point() +
  scale_x_continuous(breaks = 1:12)+
  labs(x = "Users by month",
       title =" Our Clients")+
  theme_bw()
#+
  #scale_x_continuous(breaks = 1:13)
  
```

###DURATION
```{r}
nyc_bikes_df %>% 
  summarise(average_duration_bike = mean(duration_bike))
```




#### BUSY STATIONS TO PICK UP AND LEAVE BIKES

```{r}
nyc_bikes_df %>% 
   arrange(start_station)%>% 

   

nyc_bikes_df %>% 
  count(start_station)





```


#Hire_time, mean= average, mode quitar los anos mayores de 90. 
#graph gender-type


nyc_bikes_df %>% 





Garbage
```{r}

nyc_bikes_df %>% 
  geom_line(aes(x= month, y = type, colour = gender))+
  facet_wrap(~ gender, scales = 'free_y')



```


      What is the geographical spread of the start points of bike hires?


How do you take a sample?

```{r}
leaflet(nyc_bikes_df) %>% 
  addTiles() %>% 
  addMarkers(lng =~ start_long  ,
             lat =~ start_lat)
  
```

```{r}
leaflet(nyc_bikes_df) %>% 
  #filter(start_station = 3186) %>% 
  addTiles() %>% 
  addCircleMarkers(lng =~ start_long,
             lat =~ start_lat,radius = ~ start_station ,weight = 1)
```

##which is the busiest station?

start_station
end_station


```{r}
busiest_station <- nyc_bikes_df %>% 
  group_by(start_station) %>% 
  count() %>% 
  arrange(desc(n))
busiest_station
```

```{r}
busiest_start_station <- nyc_bikes_df %>% 
  select(start_station,start_lat,start_long) %>% 
  group_by(start_station) %>% 
  count() %>% 
  arrange(desc(n))



busiest_start_station
```






```{r}
leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng =~ start_long  ,
             lat =~ start_lat)
  
```










